Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-02-26 presentation-plan/presentation-plan.tex
Add new outline for the presentation
Start adding information about the introduction of planners

\begin{itemize}
	\item Teichteil-Koenigsbuch, Florent, Guillaume Infantes, and Ugur Kuter. ``RFF: A robust, FF-based MDP planning algorithm for generating policies with low probability of failure.'' \emph{Sixth International Planning Competition at ICAPS} 8 (2008).
	\item Weld, Andrey Kolobov Mausam Daniel S. ``Determinize, Solve, and Generalize: Classical Planning for MDP Heuristics.''
\end{itemize}

@@

\begin{itemize}
	\item Introduction
	\item Brief introduction to prior knowledge
	\item Summary of the papers
	\item Advantages and disadvantages
	\item Comparison with ideas of other papers
	\item Some initial ideas of improvements
\end{itemize}

>>>>

\begin{itemize}
	\item Teichteil-Koenigsbuch, Florent, Guillaume Infantes, and Ugur Kuter. ``RFF: A robust, FF-based MDP planning algorithm for generating policies with low probability of failure.'' \emph{Sixth International Planning Competition at ICAPS} 8 (2008).
	\item Weld, Andrey Kolobov Mausam Daniel S. ``Determinize, Solve, and Generalize: Classical Planning for MDP Heuristics.''
	\item http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.83.1757\&rep=rep1\&type=pdf
	\item http://wwwold.cs.umd.edu/class/spring2004/cmsc421/planning.pdf
\end{itemize}

@@

\subsection{Introduction to a planner (A)}

Examples of planning problems:

\begin{itemize}
	\item Blocks World
	\item Motion Planning
\end{itemize}

Planning Problem:

\begin{itemize}
	\item Initial State
	\item Goal State
	\item Set of actions
\end{itemize}

Planning Plan:

\begin{itemize}
	\item Set of actions
	\item Executable in the initial state
	\item Resulting in a state that satisfies the goal state
\end{itemize}

\subsection{What is uncertainty (I)}

\subsubsection{Domains \& Applications (I)}

\subsection{Historic Overview}

\subsubsection{$<$ 1990 (A)}

\begin{itemize}
	\item STRIPS
\end{itemize}

\subsubsection{1990 - 2000 (I)}

\subsubsection{Introducing the FF planner (I)}

\subsubsection{2000 - 2005 (A)}

\subsubsection{FF-Replan (I)}

\subsubsection{RFF (A)}

\subsubsection{Compare FF-Replan with RFF (I\&A)}

\subsubsection{How did FF-Replan inspire (I)}

\subsubsection{Alternatives FF-Replan ()}

\subsubsection{What after? Any new methods (A)}

\subsection{Present goal of paper (I\&A)}

\subsection{Is it time to reconsider classical planners (I\&A)}
